Estimation of the road traffic sound levels based on Non-Negative Matrix Factorization

### 2018-01-04 paper/gloaguenNmfTraffic.tex
add experiment folder with m files (threshold initialized NMF missing for the moment)

\section{Introduction}
\subsection{Related work}
With the introduction of the European Directive 2002/EC/49, cities over 100 000 inhabitants have to produce road traffic noise maps. These maps depict an estimation of the number of city dwellers exposed to high noise levels and to draw up action plans to reduce it as too long exposures to these noises can generate health problems \cite{who_burden_2017}. These maps are the result of a simulation process based on the estimation of the traffic density on the main roads and the use of sound propagation techniques. They express $L_ {DEN}$ and $L_N$, which are \textit{Day-Evening-Night} and \textit{Night} equivalent A-weighted sound levels respectively. However, these maps introduce lot of uncertainty generated by the numerical tools \cite{van_leeuwen_noise_2015}, by the different calculation methodologies used \cite{leroy_uncertainty_2010}\cite{garg_critical_2014} or even by the calculation procedure of the number of inhabitants exposed to noise \cite{king_implementation_2011}. In addition, the usual road traffic noise maps are static, aggregating the exposure on the two indicators $L_{DEN}$ and $L_N$, thus ignoring the sound levels evolution throughout the day. Since the creation of road traffic noise maps entails long data collection and calculation times, the use of acoustic measurements could facilitate their updating or even the generation of dynamic maps \cite{wei_dynamic_2016}. These measurements can be performed at fixed stations spread all over the cities \cite{Mioduszewski} \cite{mietlicki2012innovative}, which would lead to the availability of the long-term evolution of the traffic noise levels. It can also be performed with  mobile stations \cite{can_exploring_2012} \cite{manvell2004sadmam} covering a larger area with fewer sensors but also sparse time periods. %The clustering between mobile and fixed measurements has been studied in \cite{can_measurement_2014}. \ml{je ne vois pas l'intéret de cette dernière phrase}

Currently, sensor networks in cities are spread for multiple applications (air quality assessment, measurement of meteorological parameters, ...), including the assessment of urban noise levels. DYNAMAP project \cite{dynamap_2016} studied the establishment \ml{c'est anglais ?} and feasibility of such installations. It focuses on sensor installations on specific roads at the city scale in Milan and Rome \cite{bellucci_life_2017}. In a similar way, but reduced to few neighborhoods, the CENSE project\footnote{\url{http://cense.ifsttar.fr/}} \cite{picaut2017characterization} aims to combine \textit{in situ} observations, from a sensor network, and numerical data, from noise modeling, through data assimilation techniques.

@@

\ml{tu melange contribution technique et protocole experimental, ca va pas

pas de soussection a l'intro}

We propose in this paper a method based on the Non-Negative Matrix Factorization (NMF) technique to estimate the global, $\tilde{L}_{p,traffic}$, and the 1-s equivalent, $\tilde{p}_{1s,traffic}$ sound level of the traffic through the supervised and the semi-supervised approaches as well as a method using thresholding. To validate these approaches, we consider a corpus of simulated scenes artificially created with the simulator software \textit{simScene}. The use of simulated sound scenes is necessary as it offers a full control on the design of the scenes and the knowledge of the exact contribution of the traffic component which would hardly be extracted from a recording of an urban scene ($L_{p,traffic}$ and $p_{1s,traffic}$). Both the sound scene simulation and NMF require the creation of two sound databases (figure  \ref{fig:blocDiagramNMF}). In parallel, a baseline method built from a frequency low-pass filter is computed. This method considers that road traffic is mainly composed of low frequencies and therefore can be filtered by a low-pass filter at the cut-off frequency $f_c$ (figure \ref{fig:blocDiagramFilter}). The performance of the frequency low-pass filter and NMF are then compared with the calculation of two metrics (Mean Absolute Error, normalized Root Mean Square Error).

\ml{on evite les parentheses en Anglais, pour les ref, faire , see \ref{}}

@@

where $\mathbf{W} \in \mathbb{R}^+_{F \times K}$ is the \textit{dictionary} (or basis) matrix composed of audio spectrum and $\mathbf{H} \in \mathbb{R}^+_{K \times N}$ is the \textit{activation} matrix which summarizes the temporal evolution of each element of $\mathbf{W}$ (fig.  \ref{fig:example_NMF}).

@@

Prior knowledge on the content can be adjusted with the addition of constraints (like the smoothness or the sparsness criteria \cite{virtanen_monaural_2007}) in the objective function (equation (\ref{eq:min-D-WH})) to better take account prior knowledge of the sources.

@@

\subsection{Thresholded constrained NMF}

A last approach is tested based on unsupervised NMF. Usually, $\mathbf{W}$ is learnt with the help of a learning corpus by initiated it randomly. Here, as the concerned sound source is known and audio samples of car passages are available, a initial dictionary, $\mathbf{W_0}$, is learnt by converting the audio files in the spectra domain (see part \ref{part:dictionary_learning}). Then NMF is performed where $\mathbf{W}$ (eq. \ref{eq:updateW_unsup}) and $\mathbf{H}$ (eq.  \ref{eq:updateH_Sup}) are updated alternatively. $\mathbf{W}$ is therefore updated by forcing its initiation with \textit{a priori} knowledge.

@@

\begin{equation}
\cos \theta = \frac{\mathbf{W}.\mathbf{W_0}}{\vert \vert \mathbf{W}  \vert \vert . \vert \vert \mathbf{W_0} \vert \vert}.
\end{equation}

$\cos \theta = 1$ means that the elements are identical (the $k$-th element of $\mathbf{W}$ is then considered as traffic element) whereas $\cos \theta = 0$ means that the elements are significantly different. This measure allows a bound between 1 and 0 and is an invariant scale estimation of the similarity. Then, the similarity is sorted in descending order. The elements in $\mathbf{W}$ that can belong to $\mathbf{W}_{traffic}$ are then selected by a \textit{hard thresholding} method (Figure \ref{fig:W_ThC_NMF}). It is defined as :

@@

This approach is named \textit{Thresholded constraint NMF} (ThC NMF). Other thresholding methods as the \textit{soft} \cite{donoho1995noising}and the \textit{firm} \cite{fornasier2008iterative} and multiples way to display the distance through a sigmoïd or a Radial Basis Function have been investigated. A fast parametric study has revealed that the \textit{hard} thresholding method  with a linear representation of the similarity according to $K$ (see fig. \ref{fig:W_ThC_NMF}) was the best way to get better performances.

@@

with the \textit{Traffic Interference Ratio} $TIR = \left[-12, -6, 0, 6, 12\right]$. When $TIR = -12$, the traffic component is then less present than when $TIR = 12$ where it is predominant on the \textit{interfering} class. The 1 second equivalent sound pressure level, $p_{1s,traffic}$, is also calculated (figure \ref{fig:exampleScene}). The total number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 TIR values).

@@

The second estimator is the proposed scheme, based on several flavors of the NMF framework. Multiples parameters are involved here between the dictionary learning and the own parameters of the NMF.

@@

The dictionary is built from a second sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. These records have been made on the Ifsttar's runway with the same conditions that the records made for the \textit{SimScene} database but with two different cars. First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 50 $\%$ overlap, $nfft$). Then time/frequency windows with $w_t \times F$ dimension are applied without overlapping on the spectrogram in order to consider several spectrum for each audio file. $w_t$ is fixed at $wt = [0.5 1]$ second. In each window, the root mean square value is calculated on each frequency bin to reduce the different spectrum in one spectra. Since the number of elements given by processing all the sound database is high, in order to reduce the computational and delete redundant information, a $K$-means clustering is applied to reduce the number of spectrum to $K = \left[ 25, 50, 100 \right]$. A special case is added where the root mean square of \textit{all} the spectrogram is applied. Each audio file generates one element $k$ of $\mathbf{W}$. An example that illustrates the process can be found on figure \ref{fig:dictionaryExtraction} on 3 seconds extract of a spectrogram of a car passage (fig. \ref{fig:specW}). In the case where $w_t$ = 1 second , 3 elements are therefore extracted of the spectrogram while in the case where $w_t$ = \textit{all}, all the spectrogram is reduced to one element (fig. \ref{fig:ElementW}).

@@

With the third octave spectral representation, only the case $f_c = 20$ kHz is applied. For the ThC NMF, the threshold is define between 0.20 and 0.70 with a 0.01 step. Table \ref{tab:estimation_factors} summarizes the parameters and their related values.

\begin{table*}[]
\centering
\begin{tabular}{lcccccc}
Parameter &  \multicolumn{6}{c}{value}\\ \hline
$\mathbf{TIR}$ (dB) & -12 & -6 & 0 & 6 & 12 &  \\ \hline
\textbf{sub-classes} & alert & animals & climate & humans & transportation & mechanics \\ \hline
\begin{tabular}[l]{@{}c@{}}\textbf{spectral} \\ \textbf{representation}\end{tabular} & \multicolumn{3}{c}{linear} & \multicolumn{3}{c}{third octave}\\ \hline
$\mathbf{\beta}$ & \multicolumn{3}{c}{1} & \multicolumn{3}{c}{2} \\ \hline
$\mathbf{f_c}$ (kHz) & 0.5 & 1 & 2 & 5 & 10 & 20 \\ \hline
\textbf{method} & \multicolumn{2}{c}{filter} & supervised NMF & semi-supervised NMF & ThC NMF \\ \hline
$\mathbf{t}$ & \multicolumn{6}{c}{0.20:0.01:0.70} \\ \hline
\end{tabular}
\caption{Summary of the different parameters taken into account in the frequency low-pass filter and NMF process and their values for the estimation of the traffic sound level}
\label{tab:estimation_factors}
\end{table*}

@@

In all, according Tables \ref{tab:dictionary_factors} and \ref{tab:estimation_factors}, 24540 settings are performed between the different form of the dictionary $\mathbf{W}$ (table \ref{tab:dictionary_factors}) and the multiple parameters taken into account by NMF:  for the filter estimator, between the $TIR$, the sub-classes and $f_c$, 180 settings are performed whereas for supervised and semi-supervised, 7560 associations of parameters are made. For ThC NMF, 16800 combinations can be calculated.

@@

\begin{table*}[]
\centering
\begin{tabular}{@{}cccccccc@{}}
\toprule
$\mathbf{K}$ & $\mathbf{w_t}$ (s) & $\mathbf{f_c}$ (kHz) &\begin{tabular}[c]{@{}c@{}}\textbf{spectral} \\ \textbf{representation}\end{tabular} &  $\mathbf{\beta}$ & \textbf{method} & $\mathbf{t}$ & \textbf{$MAE$ (dB)} \\ \midrule
 &  & 20 &  &  & filter &  & 4.69 ($\pm$ 4.52) \\
 &  & 0.5 &  &  & filter &  & 2.89 ($\pm$ 2.84) \\ \hline \hline
25 & all & 0.5 & linear & 1 & supervised NMF &  & \textbf{2.76 ($\pm$ 2.86)} \\
50 & 0.5 & 0.5 & linear & 2 & supervised NMF &  & \textbf{2.56 ($\pm$ 2.48)} \\
50 & 0.5 &  20 & third octave & 1 & supervised NMF &  & 3.44 ($\pm$ 3.70) \\
50 & 0.5 & 20 & third octave & 2 & supervised NMF &  & 3.02 ($\pm$ 3.33) \\ \hline \hline
100 & 0.5 &  20 & linear & 1 & semi-supervised NMF &  & \textbf{2.36 ($\pm$ 1.23)} \\
100 & 0.5 & 20 & linear & 2 & semi-supervised NMF &  & \textbf{2.34 ($\pm$ 1.35)} \\
100 & 0.5  & 20 & third octave & 1 & semi-supervised NMF &  & \textbf{2.38 ($\pm$ 1.26)} \\
100 & 0.5 & 20 & third octave & 2 & semi-supervised NMF &  & \textbf{2.43 ($\pm$ 1.43)} \\ \hline \hline
50 & all & 5 & linear & 1 & ThC NMF & 0.39 & \textbf{2.23 ($\pm$ 2.21)} \\
50 & all & 2 & linear & 2 & ThC NMF & 0.37 & \textbf{2.17 ($\pm$ 2.28)} \\
100 & all & 20 & third octave & 1 & ThC NMF & 0.57 & \textbf{2.19 ($\pm$ 2.01)} \\
100 & all & 20 & third octave & 2 & ThC NMF & 0.54 & \textbf{2.16 ($\pm$ 2.24)}\\ \bottomrule
\end{tabular}
\caption{Best results according to $\beta$, method and  spectral representation}
\label{tab:results}
\end{table*}

The two first lines show the error produced by the baseline filter. $f_c = 20 $ kHz is equivalent to consider all the sound mixtures without distinguishing the traffic from the others sound sources. Consequently, in low $TIR$ (-12 and -6), where traffic component is scarce, the error is more important than in high $TIR$ (6 and 12) where the traffic component is predominant. $f_c = 500$ Hz is the cut-off frequency with the lower mean error obtained. It is then the baseline that will be used to compare the performances of NMF. In low $TIR$, for \textit{alert} and \textit{animals}, sub-classes composed of higher frequencies, the filter is efficient as it suppress these frequency components whereas for the other sub-classes where low frequencies are present, the error is higher as the filter considers all the energy located in the pass-band and then do not dissociate the traffic element from the other sound sources. The sounds levels are then overestimate (figure \ref{fig:alert_-12}). In opposite, in high $TIR$, a low-pass filter at $f_c$ = 500 Hz removes too much energy from the traffic which has the consequence to underestimate the sound levels (figure \ref{fig:alert_12}).\\

@@

The results of different versions of NMF are summarized next to the filter results in Table \ref{tab:results_TIR}. NMF errors lower than the baseline are put in bold letter. With the exception of supervised NMF with third octave spectral representation, all NMF have a lower mean error than the baseline. The best combination is got with a ThC NMF with a third octave spectral representation, $\beta$ = 2 and a threshold $t$ = 0.54.

@@

For supervised NMF, the spectrogram $\mathbf{V}$ has to be filtered at 500 Hz to focused the reconstruction of the signals on the part where most of the traffic energy is. According to the choice of $\beta$, the dictionary parameters are different. It is the only case where it is.
In the opposite, in semi-supervised NMF, an unique set of parameters is used to get high performance : $K$ = 100, $w_t$ = 0.5 second and $f_c$ = 20 kHz. It is with $f_c = 20$ kHz that the approximation is better as it includes easily other sound sources. With a lower cut-off frequency ($ f_c <$ 5 kHz), focusing on traffic energy, the risk is then to include \textit{traffic} component in $\mathbf{W_r}$ and to deteriorate the traffic signal reconstruction. The influence of the spectral representation and $\beta$ is here weak as the errors are similar with a low standard deviation. The third approaches, ThC NMF, proposed, in the four cases, the lowest errors. Like supervised NMF, in linear spectral representation, it is necessary to filter $\mathbf{V}$ to focus on the traffic energy. Here $f_c$ is higher (5000 Hz and 2000 Hz respectively for $\beta = 1$ and $\beta$ = 2). The choice of the spectral representation influence also the order of magnitude of the threshold $t$: in the interval [0.37 0.39] and [0.54 0.57] respectively for a linear and third octave spectral representation.\\

\ml{remplacer ThC NMF par TINMF pour Thresholded initialized nmf}

For each method (supervised, semi-supervised and ThC NMF), the best parameter combinations are detailed according to the sub-classes and the $TIR$ (Table \ref{tab:results_TIR},  Figure \ref{fig:TIR_class_filter}, \ref{fig:TIR_class_sup}, \ref{fig:TIR_class_semi} and \ref{fig:TIR_class_thc}). \\

\begin{table*}[t]
\centering
\begin{tabular}{@{}cccccc@{}}
\toprule
\textbf{method} & filter & filter & supervised NMF & semi-supervised NMF & ThC NMF \\ \midrule
$f_c$ (kHz) & 20 & 0.5 & 0.5 & 20 & 20 \\
\begin{tabular}[c]{@{}c@{}}\textbf{spectral} \\ \textbf{representation}\end{tabular} &  &  & linear & linear & third octave \\
$\mathbf{\beta}$ &  &  & 2 & 2 & 2 \\ \hline
\textbf{-12} & 12.25 ($\pm$ 0.05) & 7.36 ($\pm$ 3.00) & \textbf{6.23 ($\pm$ 3.19)} &  & \textbf{5.11 ($\pm$ 3.10)} \\
\textbf{-6} & 6.96 ($\pm$ 0.05) & 3.44 ($\pm$ 1.65) & \textbf{3.00 ($\pm$ 1.39)} &  & \textbf{2.87 ($\pm$ 1.55)} \\
\textbf{0} & 3.00 ($\pm$ 0.03) & 1.17 ($\pm$ 0.24) & \textbf{1.14 ($\pm$ 0.17)} &  & 1.38 ($\pm$ 0.38) \\
\textbf{6} & 0.97 ($\pm$ 0.01) & 1.03 ($\pm$ 0.26) & \textbf{1.01 ($\pm$ 0.28)} &  & \textbf{0.70 ($\pm$ 0.32)} \\
\textbf{12} & 0.26 ($\pm$ 0.00) & 1.45 ($\pm$ 0.13) & \textbf{1.41 ($\pm$ 0.10)} &  & \textbf{0.76 ($\pm$ 0.19)} \\ \bottomrule
\end{tabular}
\caption{$MAE$ error averaged on all sub-classes on each $TIR$ for the best scenario according to each method}
\label{tab:results_TIR}
\end{table*}

@@

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/semi-sup_bar.pdf}
        \caption{Semi-supervised NMF, $\beta$ = 2, linear spectral representation, $f_c$ = 20 kHz}
                \label{fig:TIR_class_semi}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/THC_bar}
        \caption{ThC NMF, $\beta$ = 2, third octave spectral representation, $f_c$ = 20 kHz}
        \label{fig:TIR_class_thc}
    \end{subfigure}
    \caption{$MAE$ error for each sub-class and $TIR$ according to the the best results with the filter and each method (supervised, semi-supervised and ThC}
\end{figure*}

@@

The ThC NMF with a threshold fixed at $t = 0.54$, with a third octave spectral representation and $\beta$ = 2,  offers the lowest average results (Table \ref{tab:results}). According to each $TIR$, with the exception of $TIR$ = 0, all the mean errors are inferior to the baseline and supervised NMF errors. On the other hand, on low $TIR$, it does not succeed to be better than semi-supervised NMF.

>>>>

\section{Introduction}
\subsection{Related work}
With the introduction of the European Directive 2002/EC/49, cities over 100 000 inhabitants have to produce road traffic noise maps. These maps depict an estimation of the number of city dwellers exposed to high noise levels and to draw up action plans to reduce it as too long exposures to these noises can generate health problems \cite{who_burden_2017}. These maps are the result of a simulation process based on the estimation of the traffic density on the main roads and the use of sound propagation techniques. They express $L_ {DEN}$ and $L_N$, which are \textit{Day-Evening-Night} and \textit{Night} equivalent A-weighted sound levels respectively. However, these maps introduce lot of uncertainty generated by the numerical tools \cite{van_leeuwen_noise_2015}, by the different calculation methodologies used \cite{leroy_uncertainty_2010}\cite{garg_critical_2014} or even by the calculation procedure of the number of inhabitants exposed to noise \cite{king_implementation_2011}. In addition, the usual road traffic noise maps are static, aggregating the exposure on the two indicators $L_{DEN}$ and $L_N$, thus ignoring the sound levels evolution throughout the day. Since the creation of road traffic noise maps entails long data collection and calculation times, the use of acoustic measurements could facilitate their updating or even the generation of dynamic maps \cite{wei_dynamic_2016}. These measurements can be performed at fixed stations spread all over the cities \cite{Mioduszewski} \cite{mietlicki2012innovative}, which would lead to the availability of the long-term evolution of the traffic noise levels. It can also be performed with  mobile stations \cite{can_exploring_2012} \cite{manvell2004sadmam} covering a larger area with fewer sensors but also sparse time periods.

Currently, sensor networks in cities are spread for multiple applications (air quality assessment, measurement of meteorological parameters, ...), including the assessment of urban noise levels. DYNAMAP project \cite{dynamap_2016} studied the deployment and feasibility of such installations. It focuses on sensor installations on specific roads at the city scale in Milan and Rome \cite{bellucci_life_2017}. In a similar way, but reduced to few neighborhoods, the CENSE project\footnote{\url{http://cense.ifsttar.fr/}} \cite{picaut2017characterization} aims to combine \textit{in situ} observations, from a sensor network, and numerical data, from noise modeling, through data assimilation techniques.

@@

\ml{tu melange contribution technique et protocole experimental, ca va pas. pas de soussection a l'intro}

We propose in this paper a method based on the Non-Negative Matrix Factorization (NMF) technique to estimate the global, $\tilde{L}_{p,traffic}$, and the 1-s equivalent, $\tilde{p}_{1s,traffic}$ sound level of the traffic through the supervised and the semi-supervised approaches as well as a method using thresholding. To validate these approaches, we consider a corpus of simulated scenes artificially created with the simulator software \textit{simScene}. The use of simulated sound scenes is necessary as it offers a full control on the design of the scenes and the knowledge of the exact contribution of the traffic component which would hardly be extracted from a recording of an urban scene ($L_{p,traffic}$ and $p_{1s,traffic}$). Both the sound scene simulation and NMF require the creation of two sound databases; see Figure \ref{fig:blocDiagramNMF}. In parallel, a baseline method built from a frequency low-pass filter is computed. This method considers that road traffic is mainly composed of low frequencies and therefore can be filtered by a low-pass filter at the cut-off frequency $f_c$; see Figure \ref{fig:blocDiagramFilter}. The performance of the frequency low-pass filter and NMF are then compared with the calculation of two metrics (Mean Absolute Error, normalized Root Mean Square Error).

@@

where $\mathbf{W} \in \mathbb{R}^+_{F \times K}$ is the \textit{dictionary} (or basis) matrix composed of audio spectrum and $\mathbf{H} \in \mathbb{R}^+_{K \times N}$ is the \textit{activation} matrix which summarizes the temporal evolution of each element of $\mathbf{W}$. An illustrative example can be found in Figure  \ref{fig:example_NMF}.

@@

Prior knowledge on the content can be adjusted with the addition of constraints (like the smoothness or the sparsness criteria \cite{virtanen_monaural_2007}) in the objective function , see equation (\ref{eq:min-D-WH}), to better take account prior knowledge of the sources.

@@

\subsection{Thresholded initialized NMF}

A last approach is tested based on unsupervised NMF. Usually, $\mathbf{W}$ is learnt with the help of a learning corpus by initiated it randomly. Here, as the concerned sound source is known and audio samples of car passages are available, a initial dictionary, $\mathbf{W_0}$, is learnt by converting the audio files in the spectra domain; see part \ref{part:dictionary_learning}). Then NMF is performed where $\mathbf{W}$ (eq. \ref{eq:updateW_unsup}) and $\mathbf{H}$ (eq.  \ref{eq:updateH_Sup}) are updated alternatively. $\mathbf{W}$ is therefore updated by forcing its initiation with \textit{a priori} knowledge.

@@

\begin{equation}
D_{\theta}\left(\mathbf{W_0} \vert \vert \mathbf{W} \right) = \frac{\mathbf{W}.\mathbf{W_0}}{\vert \vert \mathbf{W}  \vert \vert . \vert \vert \mathbf{W_0} \vert \vert}.
\end{equation}

$D_{\theta}\left(\mathbf{W_0} \vert \vert \mathbf{W} \right) = 1$ means that the elements are identical (the $k$-th element of $\mathbf{W}$ is then considered as traffic element) whereas $D_{\theta}\left(\mathbf{W_0} \vert \vert \mathbf{W} \right)$ means that the elements are significantly different. This measure allows a bound between 1 and 0 and is an invariant scale estimation of the similarity. Then, the similarity is sorted in descending order. The elements in $\mathbf{W}$ that can belong to $\mathbf{W}_{traffic}$ are then selected by a \textit{hard thresholding} method. An illustrative example can be see in Figure \ref{fig:W_ThC_NMF}. It is defined as:

@@

This approach is named \textit{Thresholded inititialized NMF}, TI-NMF. Other thresholding methods as the \textit{soft} \cite{donoho1995noising}and the \textit{firm} \cite{fornasier2008iterative} and multiples way to display the distance through a sigmoïd or a Radial Basis Function have been investigated. A fast parametric study has revealed that the \textit{hard} thresholding method  with a linear representation of the similarity according to $K$, like in  Figure \ref{fig:W_ThC_NMF}), was the best way to get better performances.

@@

with the \textit{Traffic Interference Ratio} $TIR = \left[-12, -6, 0, 6, 12\right]$. When $TIR = -12$, the traffic component is then less present than when $TIR = 12$ where it is predominant on the \textit{interfering} class. The 1 second equivalent sound pressure level, $p_{1s,traffic}$, is also calculated ; see Figure \ref{fig:exampleScene}). The total number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 TIR values).

@@

The second estimator is the proposed scheme, based on several flavors of the NMF framework. Multiples experimental factors are involved here between the dictionary learning and the own parameters of the NMF.

@@

The dictionary is built from a second sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. These records have been made on the Ifsttar's runway with the same conditions that the records made for the \textit{SimScene} database but with two different cars. First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 50 $\%$ overlap, $nfft$). Then time/frequency windows with $w_t \times F$ dimension are applied without overlapping on the spectrogram in order to consider several spectrum for each audio file. $w_t$ is fixed at $wt = [0.5 1]$ second. In each window, the root mean square value is calculated on each frequency bin to reduce the different spectrum in one spectra. Since the number of elements given by processing all the sound database is high, in order to reduce the computational and delete redundant information, a $K$-means clustering is applied to reduce the number of spectrum to $K = \left[ 25, 50, 100 \right]$. A special case is added where the root mean square of \textit{all} the spectrogram is applied. Each audio file generates one element $k$ of $\mathbf{W}$. An example that illustrates the process can be found on figure \ref{fig:dictionaryExtraction} on 3 seconds extract of a spectrogram of a car passage ; see Figure \ref{fig:specW}. In the case where $w_t$ = 1 second , 3 elements are therefore extracted of the spectrogram while in the case where $w_t$ = \textit{all}, all the spectrogram is reduced to one element ; see Figure \ref{fig:ElementW}.

@@

With the third octave spectral representation, only the case $f_c = 20$ kHz is applied. For the TI-NMF, the threshold is define between 0.20 and 0.70 with a 0.01 step. Table \ref{tab:estimation_factors} summarizes the parameters and their related values.

\begin{table*}[]
\centering
\begin{tabular}{lcccccc}
\textbf{Experimental factors} &  \multicolumn{6}{c}{value}\\ \hline
$\mathbf{TIR}$ (dB) & -12 & -6 & 0 & 6 & 12 &  \\ \hline
\textbf{sub-classes} & alert & animals & climate & humans & transportation & mechanics \\ \hline
$\mathbf{\beta}$ & \multicolumn{3}{c}{1} & \multicolumn{3}{c}{2} \\ \hline
$\mathbf{f_c}$ (kHz) & 0.5 & 1 & 2 & 5 & 10 & 20 \\ \hline
\textbf{method} & \multicolumn{2}{c}{filter} & supervised NMF & semi-supervised NMF & TI-NMF \\ \hline
$\mathbf{t}$ & \multicolumn{6}{c}{0.20:0.01:0.70} \\ \hline
\end{tabular}
\caption{Summary of the different parameters taken into account in the frequency low-pass filter and NMF process and their values for the estimation of the traffic sound level}
\label{tab:estimation_factors}
\end{table*}

@@

In all, according Tables \ref{tab:dictionary_factors} and \ref{tab:estimation_factors}, 24540 settings are performed between the different form of the dictionary $\mathbf{W}$ (table \ref{tab:dictionary_factors}) and the multiple parameters taken into account by NMF:  for the filter estimator, between the $TIR$, the sub-classes and $f_c$, 180 settings are performed whereas for supervised and semi-supervised, 7560 associations of parameters are made. For TI-NMF, 16800 combinations can be calculated.

@@

\begin{table*}[]
\centering
\begin{tabular}{@{}cccccc@{}}
\toprule
$\mathbf{K}$ & $\mathbf{w_t}$ (s) &  $\mathbf{\beta}$ & \textbf{method} & $\mathbf{t}$ & \textbf{$MAE$ (dB)} \\ \midrule
 &  &  & filter &  & 4.69 ($\pm$ 4.52) \\
 &  &  & filter &  & 2.89 ($\pm$ 2.84) \\ \hline \hline
50 & 0.5  & 1 & supervised NMF &  & 3.44 ($\pm$ 3.70) \\
50 & 0.5  & 2 & supervised NMF &  & 3.02 ($\pm$ 3.33) \\ \hline \hline
100 & 0.5 & 1 & semi-supervised NMF &  & 2.38 ($\pm$ 1.26) \\
100 & 0.5 & 2 & semi-supervised NMF &  & 2.43 ($\pm$ 1.43) \\ \hline \hline
100 & all & 1 & TI-NMF & 0.57 & 2.19 ($\pm$ 2.01) \\
100 & all & 2 & TI-NMF & 0.54 & \textbf{2.16 ($\pm$ 2.24)}\\ \bottomrule
\end{tabular}
\caption{Best results according to $\beta$, method and  spectral representation}
\label{tab:results}
\end{table*}

The two first lines show the error produced by the baseline filter. $f_c = 20 $ kHz is equivalent to consider all the sound mixtures without distinguishing the traffic from the others sound sources. Consequently, in low $TIR$ (-12 and -6), where traffic component is scarce, the error is more important than in high $TIR$ (6 and 12) where the traffic component is predominant. $f_c = 500$ Hz is the cut-off frequency with the lower mean error obtained. It is then the baseline that will be used to compare the performances of NMF. In low $TIR$, for \textit{alert} and \textit{animals}, sub-classes composed of higher frequencies, the filter is efficient as it suppress these frequency components whereas for the other sub-classes where low frequencies are present, the error is higher as the filter considers all the energy located in the pass-band and then do not dissociate the traffic element from the other sound sources. The sounds levels are then overestimate ; see Figure \ref{fig:alert_-12}. In opposite, in high $TIR$, a low-pass filter at $f_c$ = 500 Hz removes too much energy from the traffic which has the consequence to underestimate the sound levels ; see Figure \ref{fig:alert_12}.\\

@@

The results of different versions of NMF are summarized next to the filter results in Table \ref{tab:results_TIR}. NMF errors lower than the baseline are put in bold letter. With the exception of supervised NMF with third octave spectral representation, all NMF have a lower mean error than the baseline. The best combination is got with a TI-NMF with a third octave spectral representation, $\beta$ = 2 and a threshold $t$ = 0.54.

@@

For supervised NMF, the spectrogram $\mathbf{V}$ has to be filtered at 500 Hz to focused the reconstruction of the signals on the part where most of the traffic energy is. According to the choice of $\beta$, the dictionary parameters are different. It is the only case where it is.
In the opposite, in semi-supervised NMF, an unique set of parameters is used to get high performance : $K$ = 100, $w_t$ = 0.5 second and $f_c$ = 20 kHz. It is with $f_c = 20$ kHz that the approximation is better as it includes easily other sound sources. With a lower cut-off frequency ($ f_c <$ 5 kHz), focusing on traffic energy, the risk is then to include \textit{traffic} component in $\mathbf{W_r}$ and to deteriorate the traffic signal reconstruction. The influence of the spectral representation and $\beta$ is here weak as the errors are similar with a low standard deviation. The third approaches, TI-NMF, proposed, in the four cases, the lowest errors. Like supervised NMF, in linear spectral representation, it is necessary to filter $\mathbf{V}$ to focus on the traffic energy. Here $f_c$ is higher (5000 Hz and 2000 Hz respectively for $\beta = 1$ and $\beta$ = 2). The choice of the spectral representation influence also the order of magnitude of the threshold $t$: in the interval [0.37 0.39] and [0.54 0.57] respectively for a linear and third octave spectral representation.\\

For each method (supervised, semi-supervised and TI-NMF), the best parameter combinations are detailed according to the sub-classes and the $TIR$ (Table \ref{tab:results_TIR},  Figure \ref{fig:TIR_class_filter}, \ref{fig:TIR_class_sup}, \ref{fig:TIR_class_semi} and \ref{fig:TIR_class_thc}). \\

\begin{table*}[t]
\centering
\begin{tabular}{@{}cccccc@{}}
\toprule
\textbf{method} & filter & filter & supervised NMF & semi-supervised NMF & TI-NMF \\ \midrule
$f_c$ (kHz) & 20 & 0.5 & 20 & 20 & 20 \\
$\mathbf{\beta}$ &  &  & 2 & 2 & 2 \\ \hline
\textbf{-12} & 12.25 ($\pm$ 0.05) & 7.36 ($\pm$ 3.00) & 6.23 ($\pm$ 3.19) &  & \textbf{5.11 ($\pm$ 3.10)} \\
\textbf{-6} & 6.96 ($\pm$ 0.05) & 3.44 ($\pm$ 1.65) & 3.00 ($\pm$ 1.39) &  & \textbf{2.87 ($\pm$ 1.55)} \\
\textbf{0} & 3.00 ($\pm$ 0.03) & 1.17 ($\pm$ 0.24) & \textbf{1.14 ($\pm$ 0.17)} &  & 1.38 ($\pm$ 0.38) \\
\textbf{6} & 0.97 ($\pm$ 0.01) & 1.03 ($\pm$ 0.26) & 1.01 ($\pm$ 0.28) &  & \textbf{0.70 ($\pm$ 0.32)} \\
\textbf{12} & 0.26 ($\pm$ 0.00) & 1.45 ($\pm$ 0.13) & 1.41 ($\pm$ 0.10) &  & \textbf{0.76 ($\pm$ 0.19)} \\ \bottomrule
\end{tabular}
\caption{$MAE$ error averaged on all sub-classes on each $TIR$ for the best scenario according to each method}
\label{tab:results_TIR}
\end{table*}

@@

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
      	\includegraphics[width=\linewidth]{figures/semi-sup_bar.pdf}
        \caption{Semi-supervised NMF, $\beta$ = 2, linear spectral representation, $f_c$ = 20 kHz}
                \label{fig:TIR_class_semi}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/THC_bar}
        \caption{TI-NMF, $\beta$ = 2, third octave spectral representation, $f_c$ = 20 kHz}
        \label{fig:TIR_class_thc}
    \end{subfigure}
    \caption{$MAE$ error for each sub-class and $TIR$ according to the the best results with the filter and each method (supervised, semi-supervised and ThC}
\end{figure*}

@@

The TI-NMF with a threshold fixed at $t = 0.54$, with a third octave spectral representation and $\beta$ = 2,  offers the lowest average results (Table \ref{tab:results}). According to each $TIR$, with the exception of $TIR$ = 0, all the mean errors are inferior to the baseline and supervised NMF errors. On the other hand, on low $TIR$, it does not succeed to be better than semi-supervised NMF.

Unlike supervised NMF, where $\mathbf{W}$ is fixed, and semi-supervised NMF, which combine a fixed dictionary with a mobile dictionary, TI-NMF's $\mathbf{W}$ is here update entirely to be adjusted to the scene and to adapt to the different sound environment. The closest elements of the \textit{traffic} component defined un $\mathbf{W_0}$ are then extracted to deduce the traffic signal. In Figure \ref{fig:dist_-12_12}, the similarity $D_{\theta}(\mathbf{W_0}||\mathbf{W})$ is displayed for 3 sub-classes for $TIR$ = [-12, 12].
